More than space for time: revealing the tight links constraining the temporal dynamics of network structure

### 2021-05-11 paper/manuscript.Rmd
Add spatial models

>>>>

# Methods

## Data selection

## Food-web inference

Because we had few informations about trophic interactions between resources, we
selected only the fish-fish interactions in subsequent analysis.

## Food-web and community structure

We characterized food-webs by its connectance, describing the degree of
generalism in a network [@dunne_network_2006, @delmas_analysing_2019]. It is
computed as the ratio between the actual number of links and the number of
potential links ($C = \frac{L}{S(S-1)}$, with $L$ being the number of links and
$S$ the number of trophic species). We also computed the average trophic level,
weighted by the biomass of the trophic species. The trophic level of a trophic
species is computed recursively as 1 added to the mean trophic level of the
preys that it consumes.

We described community structure by its total biomass, species richness and the
evenness of the number of individual and the amount of biomass across species. The evenness was
quantified with the Pielou index, computed as the Shannon diversity index
divided by the number of species ($P = \frac{H'}{N}$, with $H'$ being the
Shannon diversity index and $N$ the number of species).

```{r}
loadd(com_analysis_data)
```

## Classification of temporal trajectories

We characterized the temporal trajectories of network and community structure at
each site. We used a method based on second order polynomial which allows to
assess both the direction and the monotony of temporal trends
[@rigal_method_2020].

- Why do we want to classify temporal trends?
- How do we select station for each variable?

## Spatial
